---
title: "tut8"
author: "Changze Wu_1008837840"
date: "2024-03-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
```

## Q1
```{r}
data = read.csv(file = "https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/4ef82789-e038-44ef-a478-a8f3590c3eb1/resource/979fb513-5186-41e9-bb23-7b5cc6b89915/download/Pre-2023%20Apartment%20Building%20Evaluations.csv")

t.test(data$SCORE, mu = 73, alternative="greater")
t.test(data$SCORE, mu = 73, alternative="two.sided")
```
ii. The null hypothesis ($H_0$) in this case is that the population mean ($\mu$) is equal to 73. The alternative hypothesis ($H_1$) is that the population mean is greater than 73.

The p-value obtained from the t-test is less than the significance level of 0.05. Specifically, the p-value is much smaller, being < 2.2e-16 (essentially 0).

Since the p-value is less than 0.05, we reject the null hypothesis. Therefore, there is sufficient evidence to support the researcher's claim that the average score is higher than 73.

\pagebreak

## Q2
```{r}
sample_prop = mean(data$SCORE > 73)
sample_prop2 = sum(data$SCORE > 73) / length(data$SCORE)
sample_prop
sample_prop2

data_2 = data %>% summarize(n = n(), x = sum(SCORE > 73))

data_2
prop.test(data_2$x, data_2$n, p=0.5)
```

